My title

### 2024-11-27 paper/paper.qmd
finished data section rough draft

# Estimand

@@

# Data

Data analysis is performed using statistical programming language , along with packages

# Model

# Results

# Discussion

# Appendix

```{r}
#| label: cleaned_dataset-preview
#| fig-cap: "Preview of the Cleaned Dataset"
#| message: false
#| echo: false
#| warning: false

# TABLE 1: CLEANED DATASET
first_half <- data %>% select(1:6)

@@

# CONTINUTATION OF TABLE 1: CLEANED DATASET
second_half <- data %>% select(7:12)

@@

@@

summary_table <- data %>%
  filter(!is.na(rated_high)) %>%  
  group_by(rated_high) %>%       
  summarise(
    avg_pages = mean(pages, na.rm = TRUE),          
    avg_publish_year = mean(publish_year, na.rm = TRUE),
    avg_rating_count = mean(rating_count, na.rm = TRUE)  
  )

summary_table %>% 
  kable(booktabs = TRUE, linesep = "") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
```

```{r}
#| label: summary_statistic_cleaned_dataset125
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

# Create a combined scatter plot with facets
ggplot(combined_data, aes(x = publish_year, y = rating)) +
  geom_point() +
  theme_minimal() +
  facet_wrap(~group, ncol = 1, scales = "free_y") +
  geom_vline(data = avg_publish_years, aes(xintercept = avg_publish_year), 
             color = "red", linetype = "dashed", size = 1)

@@

ggplot(data2, aes(x = publish_year, y = rating)) +
  geom_point() +
  theme_minimal()

@@

avg_pages <- aggregate(pages ~ rated_high, data = data, FUN = mean, na.rm = TRUE)

ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Pages by High Rated",
    x = "High Rated (1 = Yes, 0 = No)",
    y = "Average Pages",
    fill = "High Rated"
  ) +
  theme_minimal()
```

>>>>

## Estimand

@@

The dataset used in this paper was obtained from COOKSON (CITATION), who sourced it from Goodreads (CITATION). Cookson's dataset contained over 9,000+ records of children's books that contained information on the book such as title, author, ratings, publisher and more. In the initial step, data-cleaning was performed and relevant variables were selected. First, entries with missing information were filtered out, and variables that were irrelevant to this study was also removed, which included variables such as book title. After cleaning, there were 9240 entries in the cleaned dataset.

Data analysis is performed using statistical programming language , along with packages ___

## Data Cleaning

```{r}
#| label: cleaned_dataset-preview
#| tbl-cap: "Preview of the Cleaned Children's Book Dataset"
#| message: false
#| echo: false
#| warning: false

data
# TABLE 1: CLEANED DATASET
first_half <- data %>% select(1:6)

@@

# CONTINUTATION OF TABLE 1: CLEANED DATASET
# cant fit it in one line, put it next
second_half <- data %>% select(7:12)

@@

Table 1 (CROSS REFERENCE) presents the first 5 rows from the cleaned dataset, that contains information on Children's book.

## Variable

This analysis focuses on the following variables, with a focus on `rated_high` as the dependent variable

- `rated_high`: A binary variable telling us if a book is rated high or not (above a 4 rating)
  - `0`: The book has a rating below 4
  - `1`: The book has a rating greater or equal to 4

- `pages`: An integer that represents the number of pages for the book

- `rating_count`: An integer that represents how many ratings the book received

- `publish_year`: An integer that represents the year the book was published

- `cover`: A categorical variable that represents the type of the book, which can include:
  - `Ebook`: The book is in a digital format.
  - `Kindle`: The book is only available through Kindle e-reader tablet.
  - `Board book`: The book is a picture book designed for the youngest of children, babies, infants.
  - `Hardcover`: The book has a rigid protective cover.
  - `Paperback`: The book is has a thick paper cover.

@@

summary_table <- data %>%
  filter(!is.na(rated_high)) %>%  
  group_by(rated_high) %>%       
  summarise(
    avg_pages = mean(pages, na.rm = TRUE),          
    avg_publish_year = mean(publish_year, na.rm = TRUE),
    avg_rating_count = mean(rating_count, na.rm = TRUE),
    avg_cover = names(sort(table(cover), decreasing = TRUE)[1])
  )

summary_table %>% 
  kable(booktabs = TRUE, linesep = "") %>% 
  kable_styling(bootstrap_options = "condensed", full_width = FALSE)
```

Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high rated" had more pages on average than low rated books. Furthermore, high rated books were on average published 2 years before low rated books, around the year 2003. In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x. The most common type of book cover also turned out to be hard covers. These variables are key in the analysis, and are further shown in (CITE HERE)

## Data Analysis

```{r}
#| label: fig-most-common-covers
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

(CITATION HERE PICTURE ABOVE) shows the number of cover types for "high-rated" books (rated_high = 1). It is evident that Paperback and Hardcover books make up the majority of "high-rated" books, which could potentially reflect the aesthetic and collectible value of Paperback/Hardcover books over something non-physical like an Ebook. This illustrates that physical books could be more appealing for readers due to ownership bias, greatly increasing their rating. This finding also reflects the result from (TABLE)

```{r}
#| label: fig-page-count
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
avg_pages <- aggregate(pages ~ rated_high, data = data, FUN = mean, na.rm = TRUE)

ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Pages by High Rated",
    x = "High Rated (1 = Yes, 0 = No)",
    y = "Average Pages",
    fill = "High Rated"
  ) +
  theme_minimal()

(CTATION HERE) shows that generally, "high-rated" books have more page count than low-rated books. This suggests that higher page counts could correlate with higher ratings as more pages could allow deeper storytelling, richer world-building or character development, which can result in a more immersive experience for the reader. This graph illustrates the importance for authors to use more pages for properly structured narratives.

```{r}
#| label: fig-publish-year
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

# Create a combined scatter plot with facets
ggplot(combined_data, aes(x = publish_year, y = rating)) +
  geom_point() +
  theme_minimal() +
  facet_wrap(~group, ncol = 1, scales = "free_y") +
  geom_vline(data = avg_publish_years, aes(xintercept = avg_publish_year), 
             color = "red", linetype = "dashed", size = 1) 
```
(CITATION) shows the relationship between year of publish and the book's rating. Where the horizontal axis shows the year of publishment, and vertical axis shows the rating of the book. By looking at the red line of fit (average year of publishment), "high-rated" books tend to be published before low-rated books. This could be due to selective survival where older books that remain in circulation could be considered "classics" and have stood the test of time.This is further discussed in (DISCUSSION HERE)

```{r}
#| label: fig-rating-count
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| 
data2 <- data %>% filter(rating >= 4)

ggplot(data, aes(x = rating, y = rating_count)) +
  geom_point() 
```

(FIGURE 5) shows the relationship between the rating of a book and the number of ratings it received. The red line indicates the cut-off for a book to be considered "highly-rated". It is apparent that books that are considered "highly_rated" (right of the red line) have far more ratings on average than low-rated books.

# Model {#sec-model}

# Results {#sec-result}

# Discussion {#sec-discussion}

# Appendix {#sec-appendix}

@@

@@
